Verification of the CVM algorithm with a New Recursive Analysis Technique

### 2025-02-28 isabelle/CVM_Invariant/document/root.tex
reorganise, rename, improve readme

\documentclass[11pt,a4paper]{article}
\usepackage{isabelle,isabellesym}
\usepackage{amsfonts,amsmath, amssymb,amsthm}
\usepackage[top=1.4in, bottom=1.4in, left=1.4in, right=1.4in]{geometry}

@@

In this entry, we verify the CVM algorithm's correctness using a new technique which simplifies
the formal analysis considerably compared to the orignal proof by Chakraborty et
al. The main idea is based on a probabilistic invariant that allows us to derive concentration bounds
using the Cram\'{e}r--Chernoff method.

>>>>

\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage{isabelle, isabellesym}
\usepackage{amsfonts, amsmath, amssymb, amsthm}
\usepackage[top=1.4in, bottom=1.4in, left=1.4in, right=1.4in]{geometry}

@@

In this entry, we verify the CVM algorithm's correctness using a new technique which simplifies
the analysis considerably compared to the orignal proof by Chakraborty et al. The main idea is
based on a probabilistic invariant that allows us to derive concentration bounds using the
Cram\'{e}r--Chernoff method.
